\bf\mftitle

### 2011-01-09 doc/jInfer/full/main.tex
empty skulp for vitooo
some docs

\input{00abstract}

\input{01introduction}

>>>>

\section*{Abstract}

jInfer is a framework for XML schema inference based on NetBeans platform.
Using jInfer, you can create DTD or XSD schema from your existing XML documents, schemas and queries.
With our modules, you can fine-tune the inference process and see it unfolding.
With your modules, you can do even more: export to exotic languages, try cutting-edge algorithms and more.

\paragraph{keywords:} XML, schema

\section*{Introduction}

\section*{Tutorial}
